Cover letter for ``Two applications\dots''

### 2021-03-05 papers/types2020/revisions/elab.tex

\begin{figure}
\lstinputlisting[basicstyle=\ttfamily,language=lprolog,linerange={start-end}]{code/deb-fpc.sig}
\lstinputlisting[basicstyle=\ttfamily,language=lprolog,linerange={start-end}]{code/deb-fpc.mod}
\caption{The FPC definition of De Bruijn notation as proof evidence.}
\label{fig:debruijn}
\end{figure}

@@

% LocalWords:  intuitionistic dneg peirce forall basicstyle lprolog
% LocalWords:  Elpi lc args ljf dep

>>>>

\begin{figure}
\lstinputlisting[language=lprolog,linerange={start-end}]{../code/deb-fpc.sig}
\lstinputlisting[language=lprolog,linerange={start-end}]{../code/deb-fpc.mod}
\caption{The FPC definition of De Bruijn notation as proof evidence.}
\label{fig:debruijn}
\end{figure}

@@

% LocalWords:  intuitionistic dneg peirce forall basicstyle lprolog
% LocalWords:  Elpi lc args ljf dep Coq
